Fast Algorithms for Intersection of Nonmatching Grids Using \plucker coordinates.

### 2016-09-30 paper_intersections.tex
First iteration of benchmarks.

%tables
\usepackage{booktabs}
\usepackage[vlined, linesnumbered, ruled]{algorithm2e}
%\usepackage{float}
%\newfloat{algorithm}{t}{lop}

@@

% just for our notes
\usepackage[usenames,dvipsnames]{color}   %colors

@@

To construct the Advancing front algorithm, we shall need:
\begin{itemize}
    \item \textbf{element connectivity} -- we assume this data is available from mesh preprocessing,
    \item \textbf{Axes Aligned Bounding Boxes (AABB)} -- we construct these in order to decide fastly
                    whether to compute the actual intersection of two elements,
    \item \textbf{Bounding Interval Hierarchy (BIH)} -- we alternatively create BIH above AABB to fastly search 
                    created bounding boxes for two coinciding with each other and thus obtaining a candidate pair.
\end{itemize}

@@

\section{Benchmarks}

>>>>

%tables
\usepackage{booktabs}
\usepackage[vlined, linesnumbered, ruled]{algorithm2e}
%\usepackage{float}
%\newfloat{algorithm}{t}{lop}
\usepackage{array}

@@

% just for our notes
\usepackage[usenames,dvipsnames]{xcolor}   %colors

@@

To construct the Advancing front algorithm, we shall need:
\begin{itemize}
    \item \textbf{element connectivity} -- we assume this data is available from mesh preprocessing,
    \item \textbf{Axes Aligned Bounding Boxes (AABB)} -- we construct these in order to decide fastly
                    whether to compute the actual intersection of two elements,
    \item \textbf{Bounding Interval Hierarchy (BIH)} -- we alternatively create BIH above AABB to fastly search 
                    created bounding boxes for two colliding with each other and thus obtaining a candidate pair.
\end{itemize}

@@

\section{Benchmarks}
In this section we present numerical results on several benchmark problems. At first we shall compare 
the effectivity of our fundamental algorithms for intersections with other approaches.

Next we shall compare our algorithms with different initialization phase (candidate pairs search),
and using the advancing front method or not. We shall show the results both on a mesh of a real locality
and an artificial mesh.

\subsection{Fundamental Intersection Algorithms}
The first benchmark focuses on the fundamental 1D-3D and 2D-3D intersections. We randomly generated
100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
In some of the empty cases, the bounding boxes did not collide, so the actual intersection algorithms were skipped. A single element pair was computed 100 times to obtain reasonable computational time.

\vspace{2ex}
\begin{minipage}{\textwidth}
    \centering
    \hspace{-30pt}
  \begin{minipage}[b]{0.44\textwidth}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}[b]{l|l}
            algorithm, 2D-3D& FLOPs\\
                      & estimate\\
            \hline\\
            parametric plane & 585\\
            normal plane (reuse) & 765\\
            Moller and Trumbore & 783\\
            Pl\"ucker (reuse) & 306
    \end{tabular}
    \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
                      Only 2D-3D case considered.
    \label{tab:fundamental_flops}
    \notePE{comment on different strategies}}
  \end{minipage}
  \hfil
  \begin{minipage}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}

    \captionof{figure}{Effectivity of our algorithms using \plucker coordinates in comparison to \notePE{***}.
                         One can see 1D-3D case on the left, 2D-3D on the right.}
    \label{fig:fundamental_speed}
    \end{minipage}
\end{minipage}
\vspace{2ex}

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
using \plucker coordinates, red values \notePE{***}. The gained speed up factor is approximately 5 in 1D-3D case and 2 in 1D-3D. Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.

\subsection{General algorithms}

\begin{center}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}}
        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch}} & \colorbox{orange}{BBsearch} & \colorbox{Goldenrod}{BIHonly} \\ \hline
        BIH(AABB) & AABB & BIH(AABB) \\
        AFront & AFront & ---
    \end{tabular}
\end{center}

\begin{figure}[!htb]
    \subfloat[interior fractures]{
        \includegraphics[width=0.49\textwidth]{\figpath bedrichov_fract.pdf}
        \label{fig:bedrichov_cut}
    }
    \hspace{3pt}
    \subfloat[extending fractures]{
        \includegraphics[width=0.49\textwidth]{\figpath bedrichov_fract_extend.pdf}
        \label{fig:bedrichov_extend}
    }
    \caption{A mesh of the real locality of Bed{\v r}ichov in the Jizera mountains.
             We see fractures inside the bulk mesh in the left figure,
             fractures are extending the bulk mesh.}
    \label{fig:bedrichov_meshes}
\end{figure}

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\textwidth]{\figpath intersections_bedrichov_both_speed.pdf}
    \caption{Comparison of the algorithms on meshes of Bed{\v r}ichov locality -- interior fractures on the left,
             extending fractures on the right.}
    \label{fig:bedrichov_speed}
\end{figure}

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.43\textwidth]{\figpath test1_cube0.pdf}
    \caption{Artificial mesh -- a cube with two perpendicular planes placed on the diagonals of the cube.}
    \label{fig:cube_mesh}
\end{figure}

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
    \caption{}
    \label{fig:cube_speed}
\end{figure}
